\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-21 trunk/europa.tex
updated constraint table in correct location within europa.tex and corrected arch.tex typos

In a planning problem, variable or constraint changes can come directly from an end user (by introducing new activities or goals and relating them to the rest of the plan through constraints, by changing the start time of an activity, etc), or can come from an automated planner (by expanding subgoals, introducing precedence constraints to resolve mutual exclusion conflicts, etc). When these changes happen, each Propagator is only able to ensure consistency for the constraints that are associated with it.  To maintain global consistency, the CRE implements a variant of the AC-3 algorithm \cite{mackworth77} where it asks Propagators to perform inference until the Constraint Network returns to an stable state.

@@

A \eu user can introduce new constraint types by implementing specialized Constraint and Propagator classes in C++, however, \eu provides a built-in with over 25 arithmetic, temporal, set and resource constraint types so that a large number of problem domains can be modeled without having to introduce new constraint types. \comment{insert table from http://code.google.com/p/europa-pso/wiki/ConstraintLibraryReference ? }
Temporal and resource constraints are specially important to model real-life planning domains, so it is worth going into some more detail about how \eu's built-in support works for those constraint types.

@@

Resource envelopes can be very useful when trying to figure how brittle a plan in the face of changing activity durations or start times. They can also be useful when searching for plans, although they are relatively expensive to compute so their ability to prune the search space must be weighted against the ability to search faster \comment{reference Barreiro,Morris, Bresina paper on grounded inference}.

>>>>

In a planning problem, variable or constraint changes can come
directly from an end user (by introducing new activities or goals and
relating them to the rest of the plan through constraints, by changing
the start time of an activity, etc), or can come from an automated
planner (by expanding subgoals, introducing precedence constraints to
resolve mutual exclusion conflicts, etc). When these changes happen,
each Propagator is only able to ensure consistency for the constraints
that are associated with it.  To maintain global consistency, the CRE
implements a variant of the \texttt{AC-3} algorithm \cite{mackworth77}
where it asks Propagators to perform inference until the Constraint
Network returns to an stable state.

@@

\input{constraints-table}

A \eu user can introduce new constraint types by implementing
specialized Constraint and Propagator classes in C++, however, \eu
provides a built-in with over 25 arithmetic, temporal, set and
resource constraint types so that a large number of problem domains
can be modeled without having to introduce new constraint
types. Tables \ref{tab:calconst}, \ref{tab:setconst},
\ref{tab:objhierarchy} and \ref{tab:misc} show various constraint
types.

Temporal and resource constraints are specially important to model
real-life planning domains, so it is worth going into some more detail
about how \eu's built-in support works for those constraint types.

@@

Resource envelopes can be very useful when trying to figure how
brittle a plan in the face of changing activity durations or start
times. They can also be useful when searching for plans, although they
are relatively expensive to compute so their ability to prune the
search space must be weighted against the ability to search faster
\cite{6007772}.
